Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-10-11 manuscript/main.tex
Fix typo in methods section heading
Start adding methods for antigenic drift fitness metrics

\subsection*{Phylogenetic interference}

@@

@@

>>>>

\subsection*{Phylogenetic inference}

@@

We defined the following fitness metrics per strain and timepoint.

@@

We estimated antigenic drift for each strain using either genetic or HI data.
To estimate antigenic drift with genetic data, we implemented the cross-immunity metrics originally defined by {\L}uksza and L\"assig \cite{Luksza:2014hj}.
Briefly, for each pair of strains in adjacent seasons, we counted the number of amino acid differences between the strains' HA sequences at 49 epitope sites.
We limited these pairwise comparisons to all strains sampled within the last five years from each timepoint.
For each individual strain at each timepoint, we estimated that strain's ability to escape cross-immunity by summing the exponentially-scaled epitope distances between previously circulating strains and the given strain as follows.

$$
f_{i,\mathrm{ep}}(t) = \sum_{j: t_{j} < t_{i}}{x_{j}\exp{(-D_{\mathrm{ep}}(a_{i}, a_{j}) / D_{0})}}
$$

To estimate antigenic drift with HI data, we first applied the titer tree model to the phylogeny at a given timepoint and the corresponding HI data for its strains, as previously described by Neher et al. 2016 \cite{Neher:2016hy}.
This method effectively estimated the antigenic drift associated with each branch in the phylogeny.
Next, we calculated the pairwise antigenic distance between strains as the sum of antigenic drift weights per branch on the phylogenetic path between each pair of strains.
Finally, we calculated each strain's ability to escape cross-immunity by applying the same equation as above for epitope mutations where $D_{\mathrm{ep}}(a_{i}, a_{j})$ was replaced by the pairwise antigenic distance from the tree.
